---
title: "Assignment2"
author: "Zhaoyan Ai"
date: "February 14, 2016"
output: html_document
---

1. Importing table separated value (tsv) into R as a data.frame
```{r}
raw <- read.table('http://chirayukong.github.io/infsci2725/resources/lecture4/Retention.txt', header = TRUE, sep = '\t')
```

2. General description
* Generating desciptive statistics for the data
```{r}
presum <- summary(raw) # min, max, mean, median, etc
stddev <- apply(raw, 2, sd) # standard deviation
```
* Importing library
```{r}
library('ggplot2') # importing the famous ggplot2 library
```
* Histogram for apret
```{r}
ggplot(data = raw, aes(x = apret)) + geom_histogram()
```

* Histogram for tstsc
```{r}
ggplot(data = raw, aes(x = tstsc)) + geom_histogram()
```

* Histogram for salar
```{r}
ggplot(data = raw, aes(x = salar)) + geom_histogram()
```

3. Linear regression
* Linear regression of apret on tstsc
```{r}
fit_1 = lm(apret ~ tstsc, data = raw)
summary(fit_1)
```
* Linear regression of apret on salar
```{r}
fit_2 = lm(apret ~ salar, data = raw)
summary(fit_2)
```
* Linear regression of apret on both tstsc and salar
```{r}
fit_3 = lm(apret ~ tstsc + salar, data = raw)
summary(fit_3)
```
* An overview of the pairwise relationship
```{r}
cor(raw)
```